### 2019-08-06 README.Rmd
added MAPLE

- LIME diganostics  
    - turn repetitive code into functions
    - try out different weights
    - change distance matrix in seriation to be 5-# of variables shared between two rows
    - try using distance matrix computed on the feature value with seriation
    - add in feature selection methods to LIME input options
    - think of a way to compute consistency across top two features
    - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
    - he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
    - compare the simple models based on different number of bins using an F-test
    - look into computing a diversity or consistency measure for the sensitivity analysis
    - include a penalty for the number of parameters when choosing bins
    - look at the AUC after binning
    - compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
    - try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- explainer models
    - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
    - look more into Molnar and his adviser Bernd
- understanding LIME
    - read through LIME papers again
    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
    - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
    - assess lime results on logistic regression models
    - think about how the argmin is accomplished by the LIME R package
    - try retriculate to apply python version of lime
    - look into literature on binning methods
    - think about why R^2 would be better for some binning methods
    - read new paper on Anchor
- simulation with RF
    - think about how to implement a simulation with a random forest
    - look back at 601 notes from Kaiser for model assessment
    - look at Hadley's 'removing the blindfold' for ideas
    - read book Dr. Dixon lent me on sensativity analyses
- possible improvements to LIME
    - determine the best number of bins to use for each variable
    - try out subsampling idea
- random forests confidence intervals
    - look into papers by Giles Hooker and Lucas Mentch
    - Dr. Nettleton paper

>>>>

- LIME diganostics  
    - turn repetitive code into functions
    - try out different weights
    - change distance matrix in seriation to be 5-# of variables shared between two rows
    - try using distance matrix computed on the feature value with seriation
    - add in feature selection methods to LIME input options
    - think of a way to compute consistency across top two features
    - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
    - he also suggested looking into SMOTE for dealing the inbalance in the classes with sampling
    - compare the simple models based on different number of bins using an F-test
    - look into computing a diversity or consistency measure for the sensitivity analysis
    - include a penalty for the number of parameters when choosing bins
    - look at the AUC after binning
    - compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
    - try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- explainer models
    - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
    - look more into Molnar and his adviser Bernd
    - look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
- understanding LIME
    - read through LIME papers again
    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
    - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
    - assess lime results on logistic regression models
    - think about how the argmin is accomplished by the LIME R package
    - try retriculate to apply python version of lime
    - look into literature on binning methods
    - think about why R^2 would be better for some binning methods
    - read new paper on Anchor
- simulation with RF
    - think about how to implement a simulation with a random forest
    - look back at 601 notes from Kaiser for model assessment
    - look at Hadley's 'removing the blindfold' for ideas
    - read book Dr. Dixon lent me on sensativity analyses
- possible improvements to LIME
    - determine the best number of bins to use for each variable
    - try out subsampling idea
- random forests confidence intervals
    - look into papers by Giles Hooker and Lucas Mentch
    - Dr. Nettleton paper
